Paper 2 !DRAFT! Do not circulate!

### 2014-08-05 Articles/Article_EcolEcon_2014/Paper2.Rnw
Deleted unneeded constants.

<<constants, include=FALSE, eval=TRUE>>=
# Graph Heights
# maxHeight <- 8.5 # Inches
# ninePanelScatterGraphHeight <- maxHeight # Inches

# Graph Widths
# maxWidth <- 6.5 # Inches
# fourPanelScatterGraphWidth <- maxWidth # Inches
# 
# presentationGraph1RowHeight <- 2.8 # Inches
# presentationGraph2ColWidth <- 2 # Inches
# presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
# h_param_graph <- 2.07 # Inches for a single panel
# h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
# sfParameterGraphHeight <- h_param_graph + h_param_axis
# cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
# cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
# linexParameterGraphHeight <- h_param_graph + h_param_axis
# sfParameterGraphWidth <- maxWidth
# cdParameterGraphWidth <- maxWidth
# cesParameterGraphWidth <- maxWidth
# linexParameterGraphWidth <- maxWidth
# Other graph parameters that apply to all graphs
# scaleTextSize <- 0.8  # Multiple of normal size
# scaleTickSize <- -0.5 # 50% of normal size and pointing INWARD!

spaghettiGraphLevel <- 1.0 # Spaghetti graph bands will encompass 95% of the data.
@

>>>>

<<constants, include=FALSE, eval=TRUE>>=
spaghettiGraphLevel <- 1.0 # Spaghetti graph bands will encompass 95% of the data.
@
